Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-11-30 documentation/paper.tex
Updated supervised learning summary table

When $\beta_{8}$ was used as input, position corrections were applied to the input data, as they were used for the input to Acoustic Parameter. The resulting configurations are furthermore referred to as $FourierMLP(\beta_{N})$ and $FourierMLP(PosCor(\beta_{N}, \chi))$.

@@

It became evident very quickly that a high resolution was not required to get a high accuracy relative to the ground truth data. {\it FourierMLP}$(\beta_{8})$ managed an excellent 98\% validation accuracy, and also produced a mean class-wise standard deviation of 0.29. Its very decisive prediction distribution can be observed in Figure \ref{banded_no_pos_input_hist}.

Very interestingly, {\it FourierMLP}$(\beta_{8})$ performed better than {\it FourierMLP}$(${\it PosCor}$(\beta_{8}), \chi))$, which produced an accuracy value of 96\%. Both of these results were better than any of the network architectures trained on $\omega$.

@@

Table \ref{super_overview} compares the accuracy and mean class-wise standard deviation values of certain successful supervised learning configurations with multiple input formats.

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Summary of supervised learning configurations.} \label{super_overview}
        \begin{tabular}{|l|l|l|l|l|}
            \hline
            Configuration & Max Accuracy & Precision & Recall & CWSD \\
            \hline
            {\it DeepConv}$(\omega)$ & 95\% & 97\% & 97\% & 0.52 \\
            \hline
            {\it FourierMLP}$(${\it PosCor}$(\beta_{8}))$ & 96\% & 98\% & 97\% & 0.42 \\
            \hline
            {\it FourierMLP}$(\beta_{8})$ & 98\% & 100\% & 98\% & 0.29 \\
            \hline
            {\it FourierMLP}$(\beta_{50,001})$ & 95\% & 95\% & 98\% & 0.46 \\
            \hline
            {\it ImageConv}$(\iota)$ & 68\% & 68\% & 100\% & 0.97 \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

>>>>

When $\beta_{8}$ was used as input, position corrections were applied to the input data, as they were used for the input to Acoustic Parameter. (With the position correction method currently used for PICO-60, it is currently not practical to apply it to other input formats.)

The resulting configurations are furthermore referred to as $FourierMLP(\beta_{N})$ and \\ $FourierMLP(PosCor(\beta_{N}, \chi))$.

@@

It became evident very quickly that a high resolution was not required to get a high accuracy relative to the ground truth data. {\it FourierMLP}$(PosCor(\beta_{8}))$ managed an excellent 98\% validation accuracy, and also produced a mean class-wise standard deviation of 0.29. Its very decisive prediction distribution can be observed in Figure \ref{banded_no_pos_input_hist}.

@@

Table \ref{super_overview} compares the mean accuracy, precision, recall, and class-wise standard deviation values of each of the input formats.

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Comparison of supervised learning input formats.} \label{super_overview}
        \begin{tabular}{|l|l|l|l|l|}
            \hline
            Configuration & Accuracy & Precision & Recall & CWSD \\
            \hline
            {\it DeepConv}$(\omega)$ & 87.5\% & 71.9\% & 100.0\% & 0.55 \\
            \hline
            {\it FourierMLP}$(${\it PosCor}$(\beta_{8}, \chi))$ & 96.5\% & 94.6\% & 99.7\% & 0.28 \\
            \hline
            {\it FourierMLP}$(\beta_{50,001})$ & 91.4\% & 87.8\% & 100.0\% & 0.44 \\
            \hline
            {\it ImageConv}$(\iota)$ & 63.0\% & 63.0\% & 100.0\% & 1.00 \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}
